Advantages of mixed unitary operators for quantum information processing

### 2018-12-26 decorrelation/mixed_unitaries.tex
adding in some reeferences

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.

>>>>

The past decade has seen a dramatic increase in the performance and scale of quantum information processors (QIPs). Gate fidelities are now routinely in the 99\% to 99.99\% range \cite{Barends2014, Ballance2016}, and dozens of individually-addressable qubits are becoming available on integrated devices. While these advances represent important steps forward on the path towards a computationally useful QIP, the quantum advantage milestone \cite{1203.5813} has yet to be definitively reached. The limiting factor, of course, is errors in the quantum gate operations.
